HPC--101\\Onboarding

### 2018-04-03 hpc_101/sections/02_cluster.tex
removed history, added lease option, fixed partition info

\subsection{{\craycs}}
\begin{frame}
\frametitle{{\craycs} -- History}
\begin{itemize}
\item[] 2014
  \begin{itemize}
  \item Jul. -- University of {\hawaii} (UH) selects Cray's proposal
  \item Oct. -- Delivered 184 nodes, 3,800 cores
  \item Dec. -- Passed testing and accepted
  \end{itemize}

\item[] 2015
  \begin{itemize}
  \item Jan. -- Early adopter testing started (8 users)
  \item Apr. -- Opened for general use
  \end{itemize}
\item[] 2016
  \begin{itemize}
  \item Mar. -- 92 nodes added, 5,876 cores total
  \end{itemize}
\item[] 2017
  \begin{itemize}
  \item Jan. -- 5 nodes added, 5,992 cores total
  \item May -- 5 nodes added, 6,092 cores total
  \item Jun. -- 452$+$ users have been granted access to the cluster
  \end{itemize}
\end{itemize}
\end{frame}

\subsubsection{Hardware}
\begin{frame}
  \frametitle{{\craycs} -- Compute Nodes}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{|l|l|l|l|l|l|l|l|}
        \multicolumn{8}{c}{ {\large {\textbf{ Community Nodes\footnote{\label{node_note}\tiny Nodes are diskless and run CentOS linux}} } } }\\ \hline
        \textbf{Type} & \textbf{Cores} & \textbf{Ivy-Bridge} & \textbf{Haswell} & \textbf{Broadwell} &
        \textbf{128 GB}\footnote{\label{mem_limit}\tiny Usable RAM: $\approx118$ GB of 128 GB, $\approx246$ GB of 256 GB, $\approx1003$ GB of 1 TB} & \textbf{256 GB}\textsuperscript{\ref{mem_limit}}  & \textbf{1 TB}\textsuperscript{\ref{mem_limit}}  \\ \hline
        Standard & 20 & 178 &  &  & 178 &  &  \\ \hline
        Large & 40 & 6 &  &  &  &  & 6 \\ \hline
        GPU\footnote{\label{gpu_v1}\tiny 2 x Nvidia Tesla K40} & 20 &  & 1 &  & 1 &  & \\ \hline
      \end{tabular}%
    }
  \end{table}

@@

\begin{frame}
	\frametitle{{\craycs} -- Storage}
	Two storage options are currently available on the {\craycs}
	\begin{enumerate}
		\item {\lustre}
                  \begin{itemize}
                  \item High performance parallel filesystem 
                  \item Available on all the cluster nodes
                    \item Freely available to all users
                  \end{itemize}
		\item ValueStorage
                  \begin{itemize}
                  \item Network attached scale out storage
                  \item Only available from the login nodes
                  \item Available as a for fee service
                  \end{itemize}
	\end{enumerate}
\end{frame}

@@

		\item Primarily used as scratch space for jobs (Input and Output)
		\item User do not have a usage quota (soft or hard)
		\item Certain directories are subject to a 90 day purge policy
		\item \textbf{Data is not backed up!  Users are responsible for their own data}
                \item {\lustre} utilizes RAID 6 arrays, and is fairly robust but \ldots~\\RAID is not a backup
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{{\craycs} -- Storage $\rightarrow$ ValueStorage}
        ~\\
	\begin{itemize}
		\item $500$TB of scale out storage
		\item Purchased annually in 0.5TB increments 
	\end{itemize}
	\btVFill

	\begin{center}
	\textbf{ValueStorage Pricing}~\\ 
		\resizebox{0.50\textwidth}{!}{%
		\begin{tabular}{l r }
			\toprule
			\textbf{Product} & \textbf{Annual Cost}~~ \\
	                \midrule
			\midrule
			0.5TB & \$65.00\\
                        0.5TB + Replication  & \$130.00 \\
			\bottomrule
		\end{tabular}
		}
		~\\ \href{http://www.hawaii.edu/its/value-storage-pricing/}{More Information}
		~\\	{\footnotesize \emph{All prices are subject to change}}
	\end{center}
\end{frame}

>>>>

%% \subsection{{\craycs}}
%% \begin{frame}
%% \frametitle{{\craycs} -- History}
%% \begin{itemize}
%% \item[] 2014 -- Accepted delivery of 184 nodes, 3,800 cores  
%% \item[] 2015 -- Opened for general use
%% \item[] 2016 -- 92 nodes added, 5,876 cores
%% \item[] 2017 -- 14 nodes added, 6,172 cores 
%% %\item[] 2018
%% %  \begin{itemize}
%% %  \item Apr. -- 549$+$ users have been granted access to the cluster
%% %  \end{itemize}
%% \end{itemize}
%% \end{frame}

\subsubsection{Hardware}
\begin{frame}
  \frametitle{{\craycs}}% -- Compute Nodes}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{|l|l|l|l|l|l|l|l|}
        \multicolumn{8}{c}{ {\large {\textbf{ Community Nodes\footnote{\label{node_note}\tiny Nodes are diskless and run CentOS linux}} } } } \\ \hline
        \textbf{Type} & \textbf{Cores} & \textbf{Ivy-Bridge} & \textbf{Haswell} & \textbf{Broadwell} &
        \textbf{128 GB}\footnote{\label{mem_limit}\tiny Usable RAM: $\approx118$ GB of 128 GB, $\approx246$ GB of 256 GB, $\approx1003$ GB of 1 TB} & \textbf{256 GB}\textsuperscript{\ref{mem_limit}}  & \textbf{1 TB}\textsuperscript{\ref{mem_limit}}  \\ \hline
        Standard & 20 & 178 &  &  & 178 &  &  \\ \hline
        Large & 40 & 6 &  &  &  &  & 6 \\ \hline
        GPU\footnote{\label{gpu_v1}\tiny 2 x Nvidia Tesla K40} & 20 &  & 1 &  & 1 &  & \\ \hline
      \end{tabular}%
    }
  \end{table}

@@

\begin{frame}
	\frametitle{{\craycs} -- Storage}
	Two storage options are currently available on the {\craycs}
	\begin{enumerate}
		\item {\lustre}
                  \begin{itemize}
                  \item High performance parallel filesystem 
                  \item Available on all the cluster nodes
                    \item Freely available to all users
                  \end{itemize}
		\item ValueStorage
                  \begin{itemize}
                  \item Network attached scale out storage
                  \item Only available from the login nodes
                  \item Available as a for fee service (\href{http://www.hawaii.edu/its/value-storage-pricing/}{Pricing})
                  \end{itemize}
	\end{enumerate}
\end{frame}

@@

		\item Primarily used as scratch space for jobs (Input and Output)
		\item User do not have a usage quota (soft or hard)
		\item User scratch directories are subject to a 30 day purge policy (Begins May 2nd)
		\item \textbf{Data is not backed up!  Users are responsible for their own data}
                \item {\lustre} utilizes RAID 6 arrays, and is fairly robust but \ldots~\\RAID is not a backup
	\end{itemize}
\end{frame}

%% \begin{frame}
%% 	\frametitle{{\craycs} -- Storage $\rightarrow$ ValueStorage}
%%         ~\\
%% 	\begin{itemize}
%% 		\item $500$TB of scale out storage
%% 		\item Purchased annually in 0.5TB increments 
%% 	\end{itemize}
%% 	\btVFill

%% 	\begin{center}
%% 	\textbf{ValueStorage Pricing}~\\ 
%% 		\resizebox{0.50\textwidth}{!}{%
%% 		\begin{tabular}{l r }
%% 			\toprule
%% 			\textbf{Product} & \textbf{Annual Cost}~~ \\
%% 	                \midrule
%% 			\midrule
%% 			0.5TB & \$65.00\\
%%                         0.5TB + Replication  & \$130.00 \\
%% 			\bottomrule
%% 		\end{tabular}
%% 		}
%% 		~\\ \href{http://www.hawaii.edu/its/value-storage-pricing/}{More Information}
%% 		~\\	{\footnotesize \emph{All prices are subject to change}}
%% 	\end{center}
%% \end{frame}

### 2018-04-03 hpc_101/sections/03_sustainability.tex
corrections to early slides of hpc101, addition of new members, correction to node prices.
removed history, added lease option, fixed partition info

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for free to all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, exclusive.q, lm.q, gpu.q, sb.q, kill.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

\subsubsection{Condo Model}
\begin{frame}
	\frametitle{Condo Model}
	\begin{itemize}
		\item The Condo model allows users to buy nodes (\emph{condos}) to incorporate into the cluster	
		\item Node owners are provided with priority access to their purchased hardware
		\item All nodes have a \emph{5 year warranty}
		\begin{itemize}
			\item Once a nodes warranty has expired, it will be removed from the cluster
		\end{itemize}
		\item Condo owners are given early access to purchased nodes
		  \begin{itemize}
                    \item Access is granted as soon as the funds land in our accounts
		    \item The 5 year warranty will not begin until newly ordered nodes are installed
		\end{itemize}
		\item Condo owners are also given the option to purchase~\\1TB of {\lustre} storage per node purchased
	\end{itemize}
\end{frame}

\subsubsection{Service Units}
\begin{frame}	
	\frametitle{Service Units}
	\begin{itemize}
	 \item In some cases, users will not require owning a node, but still need priority access
	 \item An alternative to purchasing a node, is to purchase service units (\emph{SU})
	 \item SUs come in two flavors:
		 \begin{itemize}
			 \item[--] Standard node units 
				\begin{itemize}
					\item 20 core hours, with access to 128GB of ram on a standard~node
				\end{itemize}
			 \item[--] Large memory node units
				\begin{itemize}
					\item 40 core hours, with access to 1TB of ram on a large~memory~node
				\end{itemize}
		 \end{itemize}
	 \item A minimum order totaling \$500 is required
	\end{itemize}
\end{frame}

\subsubsection{Price Card}
\begin{frame}
	\frametitle{Price Card}
	\begin{center}
	{\large \textbf{Condo Price Card}} \\
	\resizebox{\textwidth}{!}{%
		\begin{tabular}{l r ||l r}
			\toprule
			\textbf{Product} & \textbf{Cost} & \textbf{Product} & \textbf{Cost} \\
			\midrule
			\midrule
			Standard & \$6,600.00  & Standard + 2 GPUs (Nvidia{\regtrademark} K40) & \$13,600.00 \\
			\hline
			Large Memory & \$33,900.00  & 1 TB {\lustre} Storage for 5 years & \$$600.00$ \\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\smallskip
	\begin{center}
		{\large \textbf{Service Unit Price Card}}\\
		\begin{tabular}{l || c || r}
			\toprule
			\textbf{Product} & \textbf{Cost} & \textbf{Minimum Order}\\
			\midrule
			\midrule
			Standard node & \$0.50 per SU &  1,000~SU (\$500.00)\\
			Large memory node & \$2.00 per SU & 250~SU (\$500.00)\\
			\bottomrule
		\end{tabular}
		\btVFill
	{\footnotesize \emph{All prices are subject to change}}
	\end{center}
\end{frame}

>>>>

\section{Sustainability}
\subsection{Community Resources}
\begin{frame}
	\frametitle{Community Resources}
	\begin{itemize}
		\item The initial investment in the cluster provides resources for free to all faculty, staff, and students affiliated with the University of {\hawaii}
		\item All users can run on the publicly accessible partitions:\\ \emph{community.q, exclusive.q, lm.q, gpu.q, sb.q, kill.q, kill.gpu.q, htc.q}
		\item For some users, the publicly available resources may not be enough~\ldots
	\end{itemize}
\end{frame}

@@

\subsubsection{Condo Model}
\begin{frame}
	\frametitle{Condo Model}
	\begin{itemize}
		\item The Condo model allows users to buy nodes (\emph{condos}) to incorporate into the cluster	
		\item Node owners are provided with priority access to their purchased hardware
%		\item All nodes have a \emph{5 year warranty}
%		\begin{itemize}
%			\item Once a nodes warranty has expired, it will be removed from the cluster
%		\end{itemize}
%		\item Condo owners are given early access to purchased nodes
%		  \begin{itemize}
%                    \item Access is granted as soon as the funds land in our accounts
%		    \item The 5 year warranty will not begin until newly ordered nodes are installed
%		\end{itemize}
		\item Condo owners are also given the option to purchase~\\1TB of {\lustre} storage per node purchased
                \item {\textcolor{red}{\textbf{ Condo purchases currently suspended} }}
	\end{itemize}
        \btVFill
        \begin{center}{\footnotesize \emph{All prices are subject to change}}\end{center}
\end{frame}

\subsubsection{Node Leasing}
\begin{frame}
	\frametitle{Leasing}
	\begin{itemize}
        \item In some cases, users will not require owning a node for multiple years, but still need priority access
	\item Leases have a 1 year term
        \item Leases are $\$1,320$ per year, which is \( \frac{1}{5} \) the cost of a condo purchase
        \item Node leasees are provided priority access to their leased hardware
        \item Leases are not considered an equipment purchase
        \item Total availabity limited to $\approx100$ community nodes
	\end{itemize}
        \btVFill
        \begin{center}{\footnotesize \emph{All prices are subject to change}}\end{center}
\end{frame}

\subsubsection{Service Units}
\begin{frame}	
	\frametitle{Service Units}
	\begin{itemize}
	 \item In other cases, for users that require a large burst of dedicated nodes, service units (\emph{SU}) is an option
	 \item SUs come in two flavors:
		 \begin{itemize}
			 \item[--] Standard node units -- (\$0.50 per SU) 
				\begin{itemize}
					\item 20 core hours, with access to 128GB of ram on a standard~node
				\end{itemize}
			 \item[--] Large memory node units -- (\$2.00 per SU)
				\begin{itemize}
					\item 40 core hours, with access to 1TB of ram on a large~memory~node
				\end{itemize}
		 \end{itemize}
	 \item A minimum order totaling \$500 is required
	\end{itemize}
        \btVFill
	\begin{center}{\footnotesize \emph{All prices are subject to change}}\end{center}
\end{frame}

%% \subsubsection{Price Card}
%% \begin{frame}
%% 	\frametitle{Price Card}
%% 	\begin{center}
%% 	{\large \textbf{Condo Price Card}} \\
%% 	\resizebox{\textwidth}{!}{%
%% 		\begin{tabular}{l r ||l r}
%% 			\toprule
%% 			\textbf{Product} & \textbf{Cost} & \textbf{Product} & \textbf{Cost} \\
%% 			\midrule
%% 			\midrule
%% 			Standard & \$6,600.00  & GPU Node& Contact for pricing\\
%% 			\hline
%% 			Large Memory & \$20,000.00  & 1 TB {\lustre} Storage for 5 years & \$$600.00$ \\
%% 			\bottomrule
%% 		\end{tabular}
%% 		}
%% 	\end{center}
%% 	\smallskip
%% 	\begin{center}
%% 		{\large \textbf{Service Unit Price Card}}\\
%% 		\begin{tabular}{l || c || r}
%% 			\toprule
%% 			\textbf{Product} & \textbf{Cost} & \textbf{Minimum Order}\\
%% 			\midrule
%% 			\midrule
%% 			Standard node &  &  1,000~SU (\$500.00)\\
%% 			Large memory node & \$2.00 per SU & 250~SU (\$500.00)\\
%% 			\bottomrule
%% 		\end{tabular}
%% 		\btVFill
%% 	{\footnotesize \emph{All prices are subject to change}}
%% 	\end{center}
%% \end{frame}
